\cvsection{Work Experience}
\vspace{-2mm}

\begin{cventries}
  \cventry
    {Data Engineer}
    {President's Choice Bank}
    {Toronto, ON}
    {October 2022 - PRESENT}
    {
        \text{\bodyfontlight\bfseries Data Security \& Compliance (Tech Lead)}
        \vspace{4mm}
        \begin{cvitems}
            \item{Led enterprise-wide data masking initiative for 1,000+ BigQuery tables addressing critical security audit requirement; architected 3-phase solution (discovery, classification, protection) using Sensitive Data Protection API and Dynamic Data Masking.}
            \vspace{0.3mm}
            \item{Coordinated technical design through senior architecture review committee and collaborated with compliance, security, and audit teams to validate approach and establish Q1 2026 delivery timeline.}
            \vspace{0.3mm}
            \item{Designed centralized governance model using Data Catalog policy tags with automated discovery scans, reducing manual classification overhead across enterprise data assets.}
        \end{cvitems}
        \vspace{5mm}
        \text{\bodyfontlight\bfseries Data Platform Architecture \& Governance (Tech Lead)}
        \vspace{4mm}
        \begin{cvitems}
            \item{Led Dataplex Governance Expansion initiative; designed and built BigQuery Inventory Collector to discover and catalog metadata across all GCP projects, enabling automated governance for 1,000+ tables without manual configuration.}
            \vspace{0.3mm}
            \item{Architected end-to-end data quality framework migrating from legacy system to Dataplex; developed serverless PySpark pipeline with optimized execution (broadcast variables, memory profiling, BigQuery metrics tracking), reducing scan provisioning complexity through YAML configurations.}
            \vspace{0.3mm}
            \item{Built custom Terraform module for Auto Data Quality, simplifying scan provisioning via YAML configurations.}
            \vspace{0.3mm}
            \item{Deployed Dataplex across all environments with Data Lineage, Profiling, and Quality APIs via Terraform; implemented RBAC for user access.}
        \end{cvitems}
        \vspace{5mm}
        \text{\bodyfontlight\bfseries Production Systems \& Engineering Excellence}
        \vspace{4mm}
        \begin{cvitems}
            \item{Redesigned critical customer data processing pipeline with recurring stability issues; eliminated years of technical debt through code standardization, comprehensive documentation, and architectural simplification, achieving zero production incidents post-deployment.}
            \vspace{0.3mm}
            \item{Led analytics pipeline to production after multi-term development cycle; architected visualization-agnostic solution with centralized BigQuery calculations and caching optimizations; delivered Tableau dashboards for leadership workload tracking and initiative monitoring; mentored 5 co-ops.}
            \vspace{0.3mm}
            \item{Integrated AI tooling into development workflows to accelerate code reviews, documentation generation, and technical exploration.}
            \vspace{0.3mm}
            \item{Enhanced DAG failure reporting with metadata capture (owner, priority, business capability) enabling automated SRE alerts and Slack notifications.}
            \vspace{0.3mm}
            \item{Conducted Git workshop for 30+ business analysts covering version control concepts and GitLab best practices.}
        \end{cvitems}
        \vspace{5mm}
        \text{\bodyfontlight\bfseries Data Enablement \& Infrastructure}
        \vspace{4mm}
        \begin{cvitems}
            \item{Led initiatives building GCP tools and pipelines to optimize workflows and enhance efficiency for 50+ analysts across 8 teams.}
            \vspace{0.3mm}
            \item{Spearheaded implementation of file import solution facilitating data migration from SAS to GCP, empowering analysts to transition to cloud platform.}
            \vspace{0.3mm}
            \item{Developed and embedded SSH connectivity code into custom Airflow operators with defer mechanism, streamlining file transfers to/from GCS.}
            \vspace{0.3mm}
            \item{Pioneered callback-based audit framework for Airflow DAGs using XCom and BigQuery, establishing reusable observability pattern adopted across transfer and processing pipelines.}
        \end{cvitems}
    }
\end{cventries}
